Quality Definitions of Qualities

### 2019-10-08 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
corrected typo
added citation to definitions

Software is correct if it matches its specification.  There is no direct tool or
method for measuring correctness. One way of building confidence in correctness
is by reviewing to ensure that each requirement stated is one that the
stakeholders and experts desire.  By maintaining traceability, consistency and
unambiguity, we can reduce the occurrence of errors and make the goal of
reviewing for correctness easier.\\
 The extent to which a software's specification, design and implementation is free from errors is its correctness. The quality of a software's operation is dependent on the degree of correctness. Correctness and reliability are said to have dependencies, such that if a system exhibits a high degree of correctness then it tends to be reliable.

@@

Reliability is a critical quality for scientific software, since the results of
computations are meaningless, if they are not dependable.  Reliability is
closely tied to verifiability, since the key quality to verify is reliability,
while the act of verification itself improves reliability.\\
Reliability models can be used to predict reliability of a software product. For example measuring Mean Time to Fail (MTTF) can be a good measure for reliability

>>>>

Software is correct if it matches its specification.  There is no direct tool or
method for measuring correctness. One way of building confidence in correctness
is by reviewing to ensure that each requirement stated is one that the
stakeholders and experts desire.  By maintaining traceability, consistency and
unambiguity, we can reduce the occurrence of errors and make the goal of
reviewing for correctness easier.\\
 The extent to which a software's specification, design and implementation is free from errors is its correctness. The quality of a software's operation is dependent on the degree of correctness \cite{berander2005software}. Correctness and reliability are said to have dependencies, such that if a system exhibits a high degree of correctness then it tends to be reliable.

@@

Reliability is a critical quality for scientific software, since the results of
computations are meaningless, if they are not dependable.  Reliability is
closely tied to verifiability, since the key quality to verify is reliability,
while the act of verification itself improves reliability.\\
Reliability models can be used to predict reliability of a software product. For example measuring Mean Time to Fail (MTTF) can be a good measure of reliability \cite{berander2005software}
